Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-03-06 eswc-2012/phdsymp.tex
mention factorial designs early and restrict
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@157 43ef1190-90fd-4dd7-a769-d0121f02b80e

The problems addressed by existing benchmarks such as the ones cited
above are almost orthogonal to the problems considered by my proposed
project. While I have heard of some cases where a hypothesis test is
used to demonstrate that one implementation is better than another, it
seems not to be common practice. Furthermore, I have not to date seen
any work towards using contemporary statistical methods to evaluate
the performance of software, but I shall admit that my literature
study has been limited to RDF/OWL databases, and practical benchmarks
of databases, file systems, scientific software, etc. Therefore, the
existence of relevant references in the deeper computer science
literature is a key issue I would appreciate discussing at the
Symposium.

>>>>

The problems addressed by existing benchmarks such as the ones cited
above are almost orthogonal to the problems considered by my proposed
project. While I have heard of some cases where a hypothesis test is
used to demonstrate that one implementation is better than another, it
seems not to be common practice. Furthermore, I have not to date seen
any work towards using methods like factorial designs to evaluate
the performance of software, but there may be a limit in terms of
complexity for where it is feasible, and I will restrict myself to
SPARQL for this thesis.
